Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-04 ms_pre_post.Rmd
Some comments on the first paragraph of the Discussion

>>>>

<!---  I think these changes have been good ones, and hence that we’re heading along decent lines with the Discussion. However I think it could to with a moderately hefty edit to 1) tidy up some overarching points about what we did near the start, 2) perhaps clarify the structure of the Discussion in relation to the three questions that are now very clearly stated at the end of the Intro, and 3) tighten up the writing a bit (I can tell that the Discussion is a few iterations behind the rest of the manuscript in terms of tight and precise writing, but that’s easily fixed once we get the structure sorted). --->

<!--- Unusually for me (and sorry if this opening was my suggestion from an earlier draft!), I’m wondering whether it’s a good idea to start this broad, or whether we’d be better to keep a bit more focused to start with, and then bring in the generality after that? I’ll make some suggestions, see what you think. Writing is NOT intended to be a definitive version, just me getting some ideas down!  --->

<!--- I do think we need to get this into the start of the Discussion. It’s because our current analyses don’t play around with the magnitude of ID, it’s a fixed parameter = strong. Think we need to make sure that’s clear in peoples’ minds, otherwise we’ll get people asking about IP etc... Hence my suggestion to nail it at the start – which then mirrors the start of the Intro. --->

<!--- To me, this sentence isn’t very helpful, doesn’t say what the questions are or what we concluded, or even how we tackled them, so it seems pretty redundant. Can we weave into next section along lines suggested? --->

<!--- SUGGESTED CHANGE: Strong inbreeding depression in offspring fitness is widely hypothesised to drive evolution of both pre-copulatory and post-copulatory inbreeding avoidance, and hence drive evolution of polyandry [@Zeh1997; @Jennions2000; @Tregenza2002]. However, evolution of such degenerate (i.e. functionally overlapping) mechanisms of inbreeding avoidance cannot be presumed to occur independently, meaning that emerging reproductive strategies are likely to be shaped by relative costs, and might exhibit complex dynamic evolutionary feedbacks across multiple generations. --->

<!--- I actually don't understand the motivation behind any of these suggested changes, nor the internal logic of some of these sentences. The proposed first sentence of the introduction now shifts from talking generally about all of our results to only referring to the first stated question. The proposed second sentence is especially difficult for me -- I'm not sure how to start editing it. The second sentence suggests that evolution of degenerate traits can't be assumed to occur independently (but this is trivially true -- almost by definition! And it inverts the key logic -- the point is that traits don't have independent effects *potentially leading to degeneracy*). The next part of the second sentence suggests it necessarily follows from degeneracy that relative costs will shape reproductive interactions, but why does this have to be the case? There needs to be some logical connection between these two claims that just isn't there. I can't really figure out how to edit this because I'm really unclear as to what the logical progression of ideas is here. Can you clarify what you mean by this? --->
